\section{Limits and Colimits}

\begin{exercise}{21}
    Show that a full and faithful functor reflects the property of being a terminal (initial object).
\end{exercise}
\begin{solution}
    \begin{proof}
        Let $F\colon\Ccal\to\Dcal$ be a fully faithful functor, and $X\in\ob\Ccal$ such that $FX$ is the terminal object of $\Dcal$.
        Then for any $Y\in\Ccal$ we have $\{*\}\cong\Hom_{\Dcal}(FY, FX)\cong\Hom_{\Ccal}(Y, X)$ so $X$ is terminal in $\Ccal$. 
        We Similarly show that $F$ reflects the property of being initial.
    \end{proof}
\end{solution}


\begin{exercise}{22}
    Show that every equalizer is monic.
\end{exercise}
\begin{solution}
    \begin{proof}
        Let $e\colon E\to X$ be the equalizer of $f_1,f_2\colon X\rightrightarrows Y$, and take $g_1,g_2\colon T\to E$ such that $eg_1=eg_2$. 
        Since both $g_1$ and $g_2$ make
        \begin{tikzcd}
            E \arrow[r, "e"]                                   & X \arrow[r, "f_1", shift left] \arrow[r, "f_2"', shift right] & Y \\
            T \arrow[ru, "eg_1=eg_2"'] \arrow[u, "", dashed] &                                                               &  
        \end{tikzcd}
        commute, by uniqueness it follows that $g_1=g_2$, so $e$ is monic.
    \end{proof}
\end{solution}


\begin{exercise}{23}
    Let
    \begin{tikzcd}
        E \arrow[r, "e"] & X \arrow[r, "f_1", shift left] \arrow[r, "f_2"', shift right] & Y
    \end{tikzcd}
    be an equalizer diagram. Show that $e$ is iso if and only if $f_1=f_2$.
\end{exercise}
\begin{solution}
    \begin{proof}
        $(\Rightarrow)$ Immediate, since
        \[ f_1=f_1\id_X= f_1e\inverse e=f_2 e\inverse e = f_2\id_X=f_2.  \]

        $(\Leftarrow)$ If $f_1=f_2$ then the there exists a unique $k\colon X\to E$ such that $ek=\id_X$.
        Then $eke=e\id_E$ and since $e$ is monic by the previous exercise it follows that $ke=1_E$, so $e$ is an isomorphism.

    \end{proof}
\end{solution}

\begin{exercise}{24}
    Show that in $\Set$, every monomorphism fits into an equalizer diagram.
\end{exercise}
\begin{solution}
    \begin{proof}
        Let $f:X\to Y$ be a monomorphism in $\Set$. Define $g_1,g_2\colon Y\rightrightarrows\{0,1\}$ by $g_1(y)=1$ and
        \[ g_2(y)=\begin{cases}
            1,&y\in\im f\\
            0,&\text{otherwise}
        \end{cases}. \]
        It is clear that $g_2f=g_1f$. Let $h\colon T\to Y$ be any map such that $g_1h=g_2h$.
        It follows that $\im h\subseteq\im f$ and so we can define $k\colon T\to X$ by $k(t)=f^{-1}h(t)$.
        Then $fk=h$ and $k$ is unique, so $f$ is the equalizer of $g_1,g_2\colon Y\rightrightarrows\{0,1\}$.
    \end{proof}
\end{solution}

\begin{exercise}{25}
    Let 
    \begin{tikzcd}
        A \arrow[d, "a"] \arrow[r, "b"] & B \arrow[d, "f"] \\
        X \arrow[r, "g"]                & Y               
    \end{tikzcd}
    be a pullback diagram with $f$ monic.
    Show that $a$ is also monic.
    Also, if $f$ is iso, so is $a$.
\end{exercise}
\begin{solution}
    \begin{proof}
        Let $t_1,t_2\colon T\rightrightarrows A$ such that $at_1=at_2$.
        Then $fbt_1=gat_1=gat_2=fbt_2$ and since $f$ is monic, $bt_1=bt_2$. 
        Hence, there exists a unique $k\colon T\to A$ such that
        \begin{center}
            \begin{tikzcd}
                T \arrow[rdd, "at_1=at_2"', bend right] \arrow[rrd, "bt_1=bt_2", bend left] \arrow[rd, "k", dashed] &                                 &                  \\
                                                                                                                    & A \arrow[d, "a"] \arrow[r, "b"] & B \arrow[d, "f"] \\
                                                                                                                    & X \arrow[r, "g"]                & Y               
                \end{tikzcd}
        \end{center}
        commute. Since either $k=t_1$ or $k=t_2$ would work, it must be the case that $t_1=t_2$.
    \end{proof}
\end{solution}

\begin{exercise}{26}
    Given two commuting squares
    \begin{center}
        \begin{tikzcd}
            A \arrow[d, "a"] \arrow[r, "b"] & B \arrow[d, "f"] \arrow[r, "c"] & C \arrow[d, "d"] \\
            X \arrow[r, "g"]                & Y \arrow[r, "h"]                & Z               
        \end{tikzcd}.
    \end{center}
    Show that
    \begin{exercises}
        \item if both squares are pullback squares, then so is the composite square;
        \item if the right square and the composite square are pullbacks, then so is the left square.
    \end{exercises}

\end{exercise}
\begin{solution}
    \begin{exercises}
        \item\begin{proof}
            
        \end{proof}
        \item\begin{proof}
            
        \end{proof}
    \end{exercises}
\end{solution}

\begin{exercise}{27}
    
\end{exercise}
\begin{solution}
    \begin{proof}
        
    \end{proof}
\end{solution}

\begin{exercise}{28}
    
\end{exercise}
\begin{solution}
    \begin{proof}
        
    \end{proof}
\end{solution}

\begin{exercise}{29}
    
\end{exercise}
\begin{solution}
    \begin{proof}
        
    \end{proof}
\end{solution}

\begin{exercise}{30}
    
\end{exercise}
\begin{solution}
    \begin{proof}
        
    \end{proof}
\end{solution}